%%% start of file `template.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[13pt,a4paper,roman]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
%\usepackage{marvosym}
% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{4cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Moutupsi}
\familyname{Paul}
%\title{Resumé title}                          % optional, remove / comment the line if not wanted
\address{Chapin 2045 C, SBU}{ Stony Brook, NY-11790}    % optional, remove / comment the line if not wanted
\mobile{+1~(631)~353~8475}                     % optional, remove / comment the line if not wanted
\phone{+1~(631)~216~2512}                      % optional, remove / comment the line if not wanted
%\fax{+3~(456)~789~012}                        % optional, remove / comment the line if not wanted
\email{moutupsi.paul@stonybrook.edu}                          % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                    % optional, remove / comment the line if not wanted
%\extrainfo{additional information}            % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                  % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                            % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
I am looking for a position as a Software Engineer that best matches my skill set and explores my true potential

\section{Education}
\cventry{{\small Aug 2012--Dec 2013}}{MS in Computer Science}{SUNY Stony Brook University}{Stony Brook, NY}{\textit{3.88/4}}{Courses:  Analysis of Algorithms, Artificial Intelligence, Computer Networks, Machine Learning, Natural Language Processing, Words and Pictures (Vision and ML), Operating Systems}  

\cventry{{\small Jul 2005--Jun 2009}}{B.Tech in Computer Science}{National Institute of Technology}{Silchar, India}{\textit{8.66/10}}{}{}

\cventry{{\small Jul 2003--Jun 2005}}{High School}{Assam Higher Secondary Education Council}{Silchar, India}{\textit{84/100}}{Secured \textbf{8th position} among 100,000 candidates, \textbf{top scorer} in Physics}{}

\section{Experience}
\cventry{{\small Jun 2013--Aug 2013}}{Intern }{Microsoft}{Redmond,USA}{Bing, Indexing and Knowledge} 
{\vspace{1 mm}\normalsize Improve ranking and relevance of Related entities. Multiple data signals. Cosearch, Covisit user data, Knowledge bases like wikipedia, lastfm, Satori(Bing's knowledge graph). Improved relevance of various segments like Musicians, Movies, Movie Cast, Companies, Spouses etc.}

\vspace{3 mm}

\cventry{{\small Sep 2011--Aug 2012}}{Senior Software Developer}{Samsung Electronics}{Bangalore,India}{Common Services Framework, Smart Devices Networking} 
{\vspace{1 mm} \normalsize Converge all smart devices of a user and enable seamless interaction. Enable a rich \textbf{recommendation system} for multimedia, web content and apps. Design and develop services that can collect data from user interfaces (\textbf{Android} hand held devices, \textbf{TV}, \textbf{Chrome}). Also contributed towards exchanging \textbf{XMPP messages} between server and client.}

\vspace{3 mm}

\cventry{{\small Jun 2010--Sep 2011}}{Software Engineer}{McAfee India Pvt. Ltd}{Bangalore,India}{}{\normalsize Performance Evaluation and Functional testing}

\vspace{3 mm}

\cventry{{\small Jun 2007--Jul 2008}}{Intern}{Sun Microsystems }{India}{}{National Institute Of Technology, Campus Ambassador}{}

\section{Master's project}
\subsection{Semantic information in Word Embeddings}
\cvitem{Python, Java}{This project is done as a part of \href{https://sites.google.com/site/datascienceslab/}{\textit{Data Sciences Lab}}, Stony Brook, under the guidance of Dr. Steve Skiena. This project deals with \textbf{Embedded semantic Analysis} and \textbf{Exploring Linguistics relations in Word Embeddings}.}

\section{Other Projects}
\subsection{Webpage Classification}
\cvitem{Python, Scikit framework}{Machine Learning class project. Explored different text based features like \textbf{ngrams} and non-text features like \textbf{hyperlinks, hypertext, neighbour links} etc. using classification technique like \textbf{Naive Bayes, SVM, semisupervised learning} on CMU's WebKB dataset. }

\subsection{Timeline Detection of Movies from Scripts}
\cvitem{Java, Python }{This project explores text based features in a Movie script and  successfully use them to identify which year the movie was produced. We mainly used \textbf{statistical} and \textbf{stylometric}(style of writing) based features to help classifier distinguish between movies in different era.}

\subsection{Face recognition using captions}
\cvitem{Matlab}{In this project we expolited the caption associated with a photo to improve face recognition. We used a combination of facial features and NER. The main technique used was clustering.}

\section{Computer skills}
\cvitem{Programming}{Proficient in C and JAVA}
\cvitem{Scripting}{Proficient in Python, Worked with C\#, JavaScript, CSS, XML, HTML, MATLAB}
\cvitem{OS}{Linux, Android, Windows}
\cvitem{SCM}{Git}
\cvitem{Others}{XMPP, REST, RDF (using Jena API)}

\section{Awards and Achievements}
\cvitem{May 2010}{Awarded \textbf{best performer} during \textbf{Aricent training program} PRISM, India.}
\cvitem{May 2010}{Awarded the \textbf{best project} (Tour guide, Symbian app, Python) during \textbf{Aricent training program} PRISM, India}
\cvitem{Feb 2010}{Graduate Aptitude Test in Engineering(\textbf{GATE}) (Nation-wide test, India) with \textbf{99.89} percentile.}

\end{document}
